% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Références
\sectionTitle{Patents, Publications}{\faQuoteLeft}
\vspace{1em}
\begin{itemize}
	\item {\bf Patent:} A. Boulmakoul, S. Maguerra, et al. A Reactive Ecosytem for Complex, spatio-temporal Trajectory Analystics of infodemic propagation and infectious agents. OMPIC Patent. 2020.
	\item {\bf Patent:} S. Maguerra, et al. A Real Time Procedure to Regulate and Equilibrate Spatio-temporal Flow of Hazardous Material Transports with a Fuzzy Event-based approach Supported by the Fog Cloud. OMPIC Patent, 2018.
	\item S. Maguerra, A. Boulmakoul, and H. Badir. A Type- Level Trajectory Framework. Book chapter 8:  Intelligent Distributed Computing for Trajectories: Metamodeling, Reactive Architecture for Analytics, and Smart Applications, 2022.
	\item S. Maguerra, A. Boulmakoul, and H. Badir. Time Framework: A Type Level and Algebra Driven Design Approach. International conference on data analytics for business and industry, 2021.
	\item S. Maguerra, A. Boulmakoul, L. Karim, and H. Badir. Towards a reactive system for managing big trajectory data. J Ambient Intell Human Comput, 11, 3895–3906, 2020.
	\item S. Maguerra, A. Boulmakoul, L. Karim, and H. Badir. Towards a reactive system for managing big trajectory data. J Ambient Intell Human Comput, 11, 3895–3906, 2020.
	\item A, Boulmakoul, L, Karim, M. Nahri, S, Maguerra, and W. Basmi. Pedestrians' Space-Time-Path Trajectories: Spatiotemporal algebra and Analytics. INTIS, 2020. 
	\item S. Maguerra, A. Boulmakoul, L. Karim, and H. Badir. A Distributed Execution Pipeline for Clustering Trajectories Based on a Fuzzy Similarity Relation. Algorithms, 22 Jan. 2019.
	\item S. Maguerra, A. Boulmakoul, L. Karim, and H. Badir. A Survey on Solutions for Big Spatio-Temporal Data Processing and Analytics. 7th Edition of the INTIS Conference Proceedings, 21 Dec. 2018.
	\item S. Maguerra, A. Boulmakoul, L. Karim, and H. Badir. Scalable Solution for Profiling Potential Cyber-criminals in Twitter. 12th Edition of the ASD’2018 Conference Proceedings, 03 Mai. 2018.
	\item S. Maguerra, A. Boulmakoul, L. Karim, and H. Badir. A Survey of Spam Issue in Twitter. 14th Edition of the EDA’2018 Conference Proceedings, 04 Oct. 2018.
	\item A. Boulmakoul, S. Maguerra, L. Karim, and H. Badir. A Scalable, Distributed and Directed Fuzzy Relational Algorithm for Clustering Semantic Trajectories. 6th Edition of the INTIS Conference Proceedings, 24 Nov. 2017.
	\item S. Maguerra, A. Boulmakoul, L. Karim, and H. Badir. Real-time Distributed Architecture for the Detection, Profiling and Monitoring of Cyber-criminals in Social Networks. 4th Edition of the JDSI’17 Scientific Journey Proceedings, 04 Nov. 2017.
\end{itemize}

